The Effect of a Second AIDS Defining Illness on Survival in the MACS

### 2015-05-10 paper.Rmd
Update Table 1

@@

Survival in months.
```{r table1}
tbl.func <- function(data, col) {
    row.data <- data %>%
        group_by_(col) %>%
        summarise(col=col,
                  n=n(),
                  deaths=sum(died),
                  death.pct=mean(died),
                  surv.25=quantile(survival.time, 0.25, na.rm=TRUE),
                  surv.med=quantile(survival.time, 0.5, na.rm=TRUE),
                  surv.75=quantile(survival.time, 0.75, na.rm=TRUE))

@@

tbl.pre <- data %>%
    transmute(site=CENTER,
              race=race,
              age.ge.40=ifelse(age.at.aids >= 40,
                               "age >= 40", "age < 40"),
              aids.year=cut(year(aids.date), c(1984, 1988, 1992, 1995), 
                                 include.lowest=TRUE),
              cd4.base=cut(cd4, c(0, 50, 200, Inf), include.lowest=TRUE),
              initial.aids=frst.aids.diag,
              second.aids=sec.aids.diag,
              depressed=ifelse(depression, "depressed", "not depressed"),
              drug.user=ifelse(drug.use, "Drug User", "Not a Drug User"),
              site=CENTER,
              died=year(death.date) < 2100,
              survival.time=difftime(death.date, aids.date, 
                                     units="weeks") / 52.25 * 12,
              survival.time=as.numeric(survival.time),
              survival.time=ifelse(died, survival.time, NA))

@@

table.1 <- bind_rows(all.data,
                     tbl.func(tbl.pre, "race"),
                     tbl.func(tbl.pre, "age.ge.40"),
                     tbl.func(tbl.pre, "aids.year"),
                     tbl.func(tbl.pre, "cd4.base"),
                     tbl.func(tbl.pre, "initial.aids"),
                     tbl.func(tbl.pre, "second.aids"),
                     tbl.func(tbl.pre, "depressed"),
                     tbl.func(tbl.pre, "drug.user"),
                     tbl.func(tbl.pre, "site"))

@@

>>>>

visits <- read_csv("data/hivvert-data04.csv", progress=FALSE,
                    col_types="iiciiididdiiiiiiiddiiiiiiiiiiiidc") %>%
    filter(COHORT == 1, 
           year(mdy(VDATE)) < 1996) %>%
    mutate(year=year(mdy(VDATE))) %>%
    group_by(year) %>%
    summarise(n=n(),
              t=sum(!is.na(THRPY)),
              pct=t / n)

@@

Survival in months.
```{r table1}
tbl.func <- function(data, col, sec=FALSE) {
    row.data <- data %>%
        group_by_(col) %>%
        summarise(col=col,
                  n=n(),
                  deaths=sum(died),
                  death.pct=mean(died),
                  surv.25=quantile(survival.time, 0.25, na.rm=TRUE),
                  surv.med=quantile(survival.time, 0.5, na.rm=TRUE),
                  surv.75=quantile(survival.time, 0.75, na.rm=TRUE),
                  surv.25.2=quantile(survival.time.2, 0.25, na.rm=TRUE),
                  surv.med.2=quantile(survival.time.2, 0.5, na.rm=TRUE),
                  surv.75.2=quantile(survival.time.2, 0.75, na.rm=TRUE))

    if (sec) {
        row.data <- row.data %>%
            select(-surv.25:-surv.75) %>%
            rename(surv.25=surv.25.2,
                   surv.med=surv.med.2,
                   surv.75=surv.75.2) %>%
            filter(second.aids != "No Aids")
    } else {
        row.data <- row.data %>%
            select(-surv.25.2:-surv.75.2)
    }

@@

tbl.pre <- data %>%
    transmute(site=CENTER,
              race=race,
              age.ge.40=ifelse(age.at.aids >= 40,
                               "age >= 40", "age < 40"),
              aids.year=cut(year(aids.date), c(1984, 1988, 1992, 1995), 
                                 include.lowest=TRUE),
              cd4.base=cut(cd4, c(0, 50, 200, Inf), include.lowest=TRUE),
              initial.aids=frst.aids.diag,
              second.aids=sec.aids.diag,
              depressed=ifelse(depression, "depressed", "not depressed"),
              drug.user=ifelse(drug.use, "Drug User", "Not a Drug User"),
              site=CENTER,
              died=year(death.date) < 2100,
              survival.time=difftime(death.date, aids.date, 
                                     units="weeks") / 52.25 * 12,
              survival.time=as.numeric(survival.time),
              survival.time=ifelse(died, survival.time, NA),
              survival.time.2=difftime(death.date, sec.aids.date,
                                       units="weeks") / 52.25 * 12,
              survival.time.2=as.numeric(survival.time.2),
              survival.time.2=ifelse(died & had.sec, survival.time.2, NA))

@@

table.1 <- bind_rows(all.data,
                     tbl.func(tbl.pre, "race"),
                     tbl.func(tbl.pre, "age.ge.40"),
                     tbl.func(tbl.pre, "aids.year"),
                     tbl.func(tbl.pre, "cd4.base"),
                     tbl.func(tbl.pre, "initial.aids"),
                     tbl.func(tbl.pre, "second.aids", sec=TRUE),
                     tbl.func(tbl.pre, "depressed"),
                     tbl.func(tbl.pre, "drug.user"),
                     tbl.func(tbl.pre, "site"))

@@

```{r sens}
# do cd4 closest to 2nd aids diag instead

```
